Making ice sheet models \\ scale properly

### 2023-01-23 talk/slides.tex
fiddle with the ML slide

\begin{itemize}
\item apply \alert{machine learning}
\item \emph{concept (Jouvet et al.~2021)}: run existing non-scalable ice sheet models on a range of hypothetical/real ice sheets, and train an ML on the results
    \begin{itemize}
    \item[$\circ$] supervised learning of physically-based model yields \alert{emulator}
    \end{itemize}
\end{itemize}

\vspace{3mm}
\begin{minipage}[t][60cm][t]{\textwidth}
\begin{center}
\only<1>{\includegraphics[height=0.52\textheight]{images/tiles-jouvet.png}}
\only<2>{\includegraphics[height=0.6\textheight]{images/cnn-jouvet.png}}
\end{center}
\end{minipage}
\end{frame}

>>>>

\begin{itemize}
\item apply \alert{machine learning}
\item \emph{concept}: apply non-scalable ice sheet models on many hypothetical/real ice sheets, and train ML \alert{emulator} on results
    \begin{itemize}
    \item[$\circ$] supervised learning of physically-based model results
    \item[$\circ$] compute map on CPUs, then learn \& evaluate map on GPUs
    \item[$\circ$] convincing demo in Jouvet et al.~(2021)
    \end{itemize}
\end{itemize}

\vspace{3mm}
\begin{minipage}[t][60cm][t]{\textwidth}
\begin{center}
\only<1>{\includegraphics[height=0.52\textheight]{images/tiles-jouvet.png}}
\only<2>{\includegraphics[height=0.57\textheight]{images/cnn-jouvet.png}}
\end{center}
\end{minipage}
\end{frame}
